A neural coarse graining theory of consciousness

### 2018-05-31 Paper_neural_coarse_graining_of_consciousness.tex
After discussion for Hierarchy

			%% Story about a cell
				@ Imagining you are a neuron in (a human) Bill's brain. Your "responsibility" is to collect neurotransmitters from dendrites, accumulate membrane potential, and finally send a signal to your colleagues through an action potential.

				@ You have no idea about whether you are involved in an information processing chain for Bill to see or catch  a ball.

				@ All you have to do is receiving, computing, and outputting information.

				@ Strikingly, not only you are ignorance of Bill's intention but also Bill has no conscious awareness of your behaviour. If your work contributes some part of Bill's conscious perception or intention to act.

			%% scale
				@ \rewording{
					It seems that we cannot consciously access information at all scale. We can only be aware of information processed at a certain level of coarse-graining in the neural system.}

@@

@@

@@

		\subsection{Mathematical definition of information closure}
		\rewrite{
			The notion of informational closure refers to a situation where the information flow between the environment and the system tends to zero.
		}\cite{BERTSCHINGER.2006}

@@

		\begin{equation}
		\left.\begin{array} { r l } { J _ { n } ( E \rightarrow S ) } & { = M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) } \\ { } & { = H ( S _ { n + 1} | S _ { n } ) - H ( S _ { n + 1} | S _ { n } ,E _ { n } ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \end{array} \right.
		\end{equation}

@@

@@

			\begin{ants}
				@ Of course, from evolutional perspective, neural system should develop a better hardware to support neural coarse-graining

@@

	\section{title}

>>>>

			%% Story about a cell
				@ Imagining you are a neuron in (a human) Bill's brain. Your "responsibility" is to collect neurotransmitters through dendrites from your other neurons, accumulate membrane potential, and send a signal to other neurons through an action potential.

				@ You have no idea that you are at a neural circuit in Bill's supplementary motor area and is now involved in a motor control processing while Bill reaches his hand to grab a cup.

				@  You are totally ignorant of the intension, the goal, and the motor plan that Bill is having now even thought you are part of the physiological substrate of those "high-level" information.

				@ The same story also happens to Bill. In his conscious mind, he is not aware of what you do and even your existence if Bill never studies neuroscience.

				@ It seems that information you are processing and information shows in Bill's conscious percept are divorced from each other.

%				@ All you have to do is receiving, computing, and outputting information. 
%			
%				@ Strikingly, not only you are ignorance of Bill's intention but also Bill has no conscious awareness of your behaviour. If your work contributes some part of Bill's conscious perception or intention to act.

			%% scale

				@ It seems true that we cannot consciously access information at all scale. We can only be aware of information processed at a certain level of coarse-graining in the neural system.

@@

			%% Meaning of IC
			@ \rewrite{
				The notion of closure plays a prominent role in systems theory where it is used to identify or deﬁne the system in distinction from its environment} \cite{BERTSCHINGER.2006}

			%% Definition of IC
			@ Formally, then, a system is informationally closed if (almost) no information flows into it from the environment.

			@ \rewrite{
				The notion of informational closure refers to a situation where the information flow between the environment and the system tends to zero.} \cite{BERTSCHINGER.2006}

			@ Mathematically, information closure can be define and measured by as the degree of information flowing from the environment to a system.
				\begin{equation}
					\left.\begin{array} { r l } { J _ { n } ( E \rightarrow S ) } & { = M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) } \\ { } & { = H ( S _ { n + 1} | S _ { n } ) - H ( S _ { n + 1} | S _ { n } ,E _ { n } ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \end{array} \right.
				\end{equation}

@@

		% **************************************************************************** %

@@

		\subsection{Mathematical definition of information closure}

@@

@@

		\begin{figure}[h]
			\includegraphics[width=\textwidth]{CGandIC.png}
			\caption{information closure through neural coarse-graining}
			\label{fig:CGandIC}
		\end{figure}

@@

			\begin{figure}[h]
				\includegraphics[width=\textwidth]{hierarchy.pdf}
				{Coarse-grain and sensory anatomical hierarchies}
				\label{fig:hierarchy}
			\end{figure}

			\begin{figure}[h]
				\includegraphics[width=\textwidth]{WritingMaterials/HierachyDiscussion (1).jpg}
%				{Coarse-grain and sensory anatomical hierarchies}
			\end{figure}

			\begin{ants}
				@ It's important to note that the dimension coarse-graining direction is not necessary to be align with anatomical sensory hierarchy in the neural system.

				@ For example, pooling layers in CNN is an implementation of coarse-graining function. It' is very plausible visual processing hierarchy in the neural system realises pooling layers.

				@ Of course, from evolutional perspective, neural system should develop a better hardware to support neural coarse-graining

@@
